%student-created design problems from previous terms

\documentclass{article}

\usepackage{course}
\usepackage{verbatim}
\usepackage{fullpage}

\def\handout{More design problems}
\def\coursenum{142}
\def\coursetitle{Program design and methodology}
\def\courseterm{Spring}
\def\courseyear{2025}
\parskip 6pt
\parindent 0pt

\begin{document}

Describe how you could solve each of the following problems using data
structures we've learned so far.
Specify the ADTs (List, Stack, Queue, Iterator, Set, Map, Priority Queue) you
would use and how to use them to efficiently support the required
operations.

\begin{enumerate}

\item
Imagine you are a doctor who advises people with prediabetes. The most
important part of controlling the
disease is analyzing the dependency of the food a patient eats to
their blood sugar. To prevent diabetes, a
patient should figure out how each food affects their blood
sugar. To help them do it, you decided to
create the application that stores the name of the food that was eaten
by the patient and what was their
blood sugar after the consumption. Then, the next time a patient wants
to eat this food, they can check
how it affects their blood sugar before they eat it. You give them the
application and tell them to store the
name of the food and values of their sugar levels every time they try
to eat something new.
What ADT(s) would you use to implement this app?
%map from string (food name) to integer (blood sugar reading)

\item 
Happy Vet is the busiest vet clinic in town. Everyday they have a
lineup of regular health check-ups, however sometimes there are cases
that require immediate action. Each vet at Happy Vet has their own
tablet that lets them know who their next client is. The tablet has
the name of the client, the type of visit needed, emergency or
regular, and a description of the help needed. As long as there are no
emergencies the vet will see that their next client is a regular
health checkup. When there is an emergency they will have to take care
of that case first before returning to the regular check-ups. If there
is more than one emergency at a time each veterinarian will take the
next case that is marked as an emergency before returning to the
regular health checkups. If they fall behind on the emergencies then
each vet will continue to take the oldest emergency available. If they
fall behind on regular checkups they will finish the emergencies and
then start in on the oldest regular checkup available.
What ADTs would you use to implement this sytem?
%2 queues

\item 
I need a program that allows me to feed my rats fairly every
time it’s treat time. The same rat should not be first everytime, so
they each need a turn to get fed first. (Basically, if a rat is fed
first this time, it moves to the last place on the next feeding and
all the other rats move one position earlier.)
The exception is that rats who are sick or injured should have
priority and should be fed first.
The program should read in the rats in alphabetical order by name
along with their position in the feeding order last time and whether
they are sick or injured.
Then it should output the order in which the rats should be fed this
time.
How would you implement this?
%priority queue- queue doesn't work because order of reading them is
%different than the output order 

\item 
You work for a minor league sports team. The team is getting a new
mascot. The organization decides to hold a contest where fans submit
suggestions for the name of the new mascot. Anyone who chooses to
participate must say the name they think the new mascot should have
with a brief reasoning for why they think it's a good
name. Suggestions would then be sent to a group of panelists who would
select their favorite. The contest was much more popular than the team
imagined, and they are getting lots of duplicate names. Even if two
entries suggest the same name, the panelists would still like to read
the multiple arguments different people make for the name. You are in
charge of making a program that allows the panelists to look at each
name one at a time, together with all the arguments submitted with
that name.
What ADT(s) would you use to implement this program?
%map from name to list of reasonings

\item  
You are a director of an American Legion Baseball Tournament and have
to set up the end of year baseball tournament for all the teams in
your state.
Part of this is to maintain that statistics for each player such as
homeruns, hits, and strikeouts.
For pitchers, the system also needs to record wins, losses, innings pitched,
and ERA.
All of these stats would be tied to a player's name (we assume unique
names), with updates happening as the game is played.
For example, when a player makes a hit, your system must be able to
update this stat.
%map from name to stats

\item 
A streamer is currently streaming Mega Man 8-bit Deathmatch online
matches and is finding it difficult to choose a character to play as.
To solve this issue, the streamer decides to create a program that allows
all of his or hers viewers, regardless of their subscription status,
to submit character requests.
The program will order these character requests and print them to the
streamer in the order to play them.
The order will mostly be oldest to the newest except that character
requests submitted by viewers who are
subscribed to the streamer have priority over those submitted by
viewers without a subscription.
In other words, the list will include character requests submitted by subscribers, in the order of the oldest to the
newest, are presented to the streamer, and then character requests from regular viewers, in the order of the oldest to the newest.
%two queues  

\end{enumerate}

\end{document}
